Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2021-02-02 SIR_manuscript.tex
working on discussion

We compared two testing strategies, random and \emph{tergeted}, by incorporating the compartment-specific relative testing weights $W_S$, $W_I$ and $W_R$. Although, in this study for the purpose of simplicity and illustraition, we assumed $W_I/W_S=3$ for the targeted strategy scenario, we have not specified a particular relative testing weights corresponding to a particular targeted testing scenario. 
Modeling different targeted testing strategies, thus test-specific testing weights, requires prior information of the conditional probabilities of getting tested for people in a given compartment. This part needs to be developed further in future work. 
This can be implied when we would like to quantify and compare the effect of different levels of test forcus for infectious people on the basic reproduction number $\Rnum$, and conclude about the disease spread management. For example, when people are tested for "screening", the individuals with potential higher mobility, eg. people who are getting on flights, get more tested and thus the coresponding heavier testing weight is assigned than people awaiting for a surgery and are probably going to stay in a long-term care facility and consequently less mobile and more isolated to begin with. With our model, we would be able to compare the sensitivity of the disease dynamics, through $\Rnum$, with respect to testing processes.

{\bf \percap testing intensity, $\rho$};
Proposition \ref{prop1} part \ref{p1:rho} indicates that increasing testing intensity $\rho$ reduces $\Rnum$. This is sensible since as people are moved to test compartments, namely $I_p$ and $I_n$ in particular, may partially or fully self-isolate, and individuals who have tested positive, namely $I_c$ compartment, are highly likely to self-isolate. The higher probability of being subject to isolation, the lower the transmission \eqref{Lambda} will become and the lower $\Rnum$ will become. Our simulation supports this fact. However, it appeared to be hard to conclude this by directly differentiating the expression of $\Rnum$ due to its complexity.

>>>>

We incorporated the compartment-specific relative testing weights, $W_S$, $W_I$ and $W_R$, to model random testing and \emph{targeted} testing strategies. Here, in the case of targeted testing and for the simplicity and illustraition purposes, we assumed that infected and recovered individuals are tested at three times the \percap rate of susceptible individuals, i.e., $W_I/W_S=3$ and $W_R=W_I$. Note we have not specified a methodology to assigne particular relative testing weights corresponding to a particular targeted testing scenario. 
This part needs to be developed further in future work. 
Modeling different targeted testing strategies, thus test-specific testing weights, requires prior information of the conditional probabilities of getting tested for people in a given compartment. 
This can be implied when we would like to quantify and compare the effect of different levels of test forcus for infectious people on the basic reproduction number $\Rnum$, and conclude about the disease spread management. For example, when people are tested for "screening", the individuals with potential higher mobility, eg. people who are getting on flights, get more tested and thus the coresponding heavier testing weight is assigned than people awaiting for a surgery and are probably going to stay in a long-term care facility and consequently less mobile and more isolated to begin with. With our model, we would be able to compare the sensitivity of the disease dynamics, through $\Rnum$, with respect to testing processes.

{\bf The \percap testing intensity, $\rho$;}
Proposition \ref{prop1}, part \ref{p1:rho}, and also Figure \ref{pan} indicates that increasing testing intensity $\rho$ reduces $\Rnum$. This is sensible since as people are moved to test compartments, namely $Z_p$ and $Z_n$ for $Z \in \{S,I,R\}$, they may partially or fully self-isolate. Also individuals who have tested positive, namely $Z_c$ compartment for $Z \in \{S,I,R\}$, are highly likely to self-isolate. The higher probability of being subject to isolation, the lower the force of infection \eqref{Lambda} and the lower $\Rnum$ will become. While our simulation supported this result, analytically it appeared to be hard to conclude this due to the complexity of $\Rnum$ expression.
